page 13-15

Admin Stuff 

\subsection{Results of Prior NSF Support}
\markup{Need to add VTS travel award, and MRI}

The PI's prior NSF support in the last 5 years:

{
	\noindent 1.	\textbf{Title:} EARS: Adaptive Behavioral Responses for Dynamic Spectrum 
	Access-Based Connected 
	Vehicle Networks. \textbf{Total Award Amount:} \$299,840.00 \textbf{Total Award Period 
		Covered:} 01/01/16 -
	12/31/18.
	\textbf{Investigators: }PI: Alexander M. Wyglinski, Co-PI: Robert Gegear, Co-PI: Elizabeth 
	Ryder. 
	Currently project studies how dynamic spectrum access (DSA)-based vehicular networks can be 
	combined with foraging theory concepts employed by bumblebees. Resulting publication: [6]. 
	NSF award number 1547291. 
	
	\noindent 2.	\textbf{Title:} WiFiUS: Collaborative Research: Future Small-Cell Networks 
	Using Reconfigurable 
	Antennas.
	\textbf{Total Award Amount:} \$90,161 \textbf{Total Award Period Covered:} 02/01/15 -
	01/31/17. 
	Investigators: PI: A. M. Wyglinski.
	Currently developing practical reconfigurable antennas and transceiver processing techniques 
	for small-cell base stations. Resulting publications: [1-5]. NSF award 
	number 1457310.
	
	\noindent 3. \textbf{Title:} STTR Phase II: Reconfigurable Wireless Platforms for Spectrally 
	Agile Coexistence.
	\textbf{Total Award Amount:} \$748,847 \textbf{Total Award Period Covered:} 04/15/14 -
	09/31/16.
	\textbf{Investigators:} PI: Samuel MacMullen, Co-PI: A. M. Wyglinski.
	Currently developing digital predistortion strategies for spectrally agile transceivers using 
	non-contiguous portions of spectrum in parallel for high-speed data transmission. Resulting 
	publications: [7] NSF award number 1353600.
	
	\noindent 4.	\textbf{Title:} STTR Phase I: Reconfigurable Wireless Platforms for Spectrally 
	Agile Coexistence.
	\textbf{Total Award Amount:} \$150,000 \textbf{Total Award Period Covered:} 07/01/12 - 
	06/31/13.
	\textbf{Investigators:} PI: Samuel MacMullen, Co-PI: A. M. Wyglinski.
	Developed a functional prototype of a spectrally agile transceiver that would be able to use 
	non-contiguous portions of spectrum in parallel for high-speed data transmission. Resulting 
	publications: [118]. NSF award number 1212340.
}
